Reproducibility in plant pathology: where do we stand and a way forward

### 2021-10-15 analysis/paper/paper.Rmd
Update keywords
Remove colophon for submission

**Keywords: open science, open data, reproducible research, FAIR data**

@@

# Colophon

This report was generated on $`r Sys.time()`$ using the following computational environment and dependencies:

```{r colophon, cache = FALSE}
# which R packages and versions?
sessioninfo::session_info()
```

The current Git commit details are:

```{r}
# what commit is this file at? You may need to change the path value
# if your Rmd is not in analysis/paper/
git2r::repository("../..")
```

>>>>

**Keywords: Data Science, Computational Biology, Techniques**

@@
